A fast unified model for parsing and sentence understanding

### 2016-03-18 writing/hard_stack_paper/paper.tex
Typo: more larger -> larger

We suspect that the hybrid nature of the full SPINN model is also responsible for its ability to perform better than an RNN baseline even when its internal parser is relatively ineffective at producing correct full-sentence parses. We suspect that it is acting somewhat like the Tree-based CNN, only with access to more larger trees: Using tree structure to build up local phrase meanings, and then using the tracking LSTM, at least in part, to combine those meanings.

>>>>

We suspect that the hybrid nature of the full SPINN model is also responsible for its ability to perform better than an RNN baseline even when its internal parser is relatively ineffective at producing correct full-sentence parses. We suspect that it is acting somewhat like the Tree-based CNN, only with access to larger trees: Using tree structure to build up local phrase meanings, and then using the tracking LSTM, at least in part, to combine those meanings.
